Simulating High-Dimensional Multivariate Data

### 2020-10-30 040-monte-carlo-evaluation.Rmd
bigsimr MC studies draft

Before applying our methodology to real data simulation, we conduct several Monte Carlo studies to investigate method performance in comparison to other existing implementations. 
We focus the numerical experiments on assessing how well the procedure scales to high dimension with respect to reasonable computation times (property S1 above) and accurately matching marginal and dependency parameters. 
The simulations will proceed in increasing complexity --- leading up to the setting in our motivating example. 
We begin by exploring simple exchangeable (constant) correlation structures under a large number of simulation replicates while applying the algorithm above to first continuous then discrete marginal distributions to test the robustness of our algorithm since exact matching is not guaranteed.

@@

@@

@@

@@

@@

>>>>

Before applying our methodology to real data simulation, we conduct several Monte Carlo studies to investigate method performance.
Since marginal parameter matching in our scheme is essentially a sequence of univariate inverse probability transforms, the challenging aspects are the accuracy of dependency matching and computational efficiency.
And, so, we'll focus the numerical experiments on assessing how well the procedure scales to high dimension with respect to reasonable computation times (property S1 above) and accurately matching marginal and dependency parameters.

Further, we select simulaiton configurations to ultimately simulate discrete-valued RNA-seq data and the simulations will proceed in increasing complexity, leading to our motivating application in Section \@ref(examples). 
We begin wiith empirically evaluating the dependency matching across all three supported correlations --- Pearson's, Spearman's, and Kendall's ---- in identical, bivariate marginal configurations.
The simulations progress from bivariate normal, to bivariate gamma (non-normal yet continuous), and bivariate negative binomial (mimicking RNA-seq counts).

@@

Figure \@ref(fig:ch040-biNormPlot) `bigsimr` recovers the Pearson specified correlations for MVN.

@@

Figure \@ref(fig:ch040-biGammaPlot) `bigsimr` recovers the Pearson specified correlations for bivariate gamma.

@@

Figure \@ref(fig:ch040-biNegBinPlot) `bigsimr` recovers the Pearson specified correlations for bivariate negative binomial.

@@

Taken together, the studies show our methology are accuracy across the entire range of possible correlation values for the rank-based dependency measures in continuous marginals.
For all selected bivariate marginals, the Pearson correlation matching is approximate.
For discrete margins, matching the dependency measures was somewhat less accurate, even for the rank-based metrics, especially near the correlation bounds.
Yet generally the accuracy seems adequate for most applications, at least in these limited simulation settings.

Of course, one could choose marginals that lead to poor matching by construction.
In partice, we recommend users to always evaluate the accuracy for their application, using methods similar to those presented above.
See [Discusion](discussion) for future directions for fast Pearson matching and discrete-specific modifications.

@@

The bivariate simulations provide a low-dimensional perspectitive.
But, of course, this is not `bigsimr`'s primary purpose.
We'd like the random vector methodolgy to scale to high-dimensional problems.

DESCRIBE WHAT WE DID. Do we need to redo this?

### 2020-10-30 060-conclusion-discussion.Rmd
bigsimr MC studies draft

- mention that `bigsimr`

Nvidia-based(copyright symbol) graphical-processing-unit (GPU), OpenCL future direction.

>>>>

- mention that `bigsimr`   
- comparison to other existing implementations see @Li2019gpu. copula
Nvidia-based(copyright symbol) graphical-processing-unit (GPU), OpenCL future direction.
- discrete matching in RNA-seq simulation may be due to large counts and ties could greatly affect
